Ms 1

### 2017-11-27 ms1/ms1_display.Rmd
minor

drug_trends = read_tsv('tables/trend_models.tsv') %>%
  filter(term=='year') %>%
  arrange(estimate) %>%
  mutate(estimate=3*estimate,
         std.error=sqrt(3)*std.error) %>%
  mutate(ci=1.96*std.error,
         ci_lo=estimate-ci,
         ci_hi=estimate+ci) %>%
  mutate(y=est2pct(estimate),
         ymin=est2pct(ci_lo),
         ymax=est2pct(ci_hi)) %>%
  mutate(change=sprintf('%.2f (%.2f -- %.2f)', y, ymin, ymax))
```

```{r drug_trends_display}
format_p = function(p) {
  if_else(p < 0.001, '< 0.001', as.character(round(p, 3)))
}

drug_trends %>%
  filter(abx != 'overall_wrefill') %>%
  mutate(adj.p=p.adjust(p.value, method='BH')) %>%
  select(abx, y, ymin, ymax, p.value) %>%
  mutate_at(vars(y, ymin, ymax), function(x) format(x, digits=2, nsmall=2)) %>%
  mutate(p.value=format_p(p.value)) %>%
  kable(caption='Drug trends: Percent change from 2011 to 2014')

drug_trends %>%
  filter(abx != 'overall_wrefill') %>%
  # put the abx in order
  arrange(desc(y)) %>%
  mutate(abx=fct_inorder(factor(abx))) %>%
  mutate(abx=fct_relevel(abx, c('overall', 'overall_inapprop', 'overall_approp'))) %>%
  mutate(abx=fct_rev(abx)) %>%
  # plot
  ggplot(aes(x=abx, y=y, ymin=ymin, ymax=ymax)) +
  geom_bar(stat='identity', fill='white', color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in consumption 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 32.5), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```

@@

@@

dx_to_pde_trends = read_tsv('tables/dx_to_pde_trends.tsv') %>%
  filter(term=='year') %>%
  mutate(estimate=3*estimate,
         std.error=sqrt(3)*std.error) %>%
  mutate(ci=1.96*std.error,
         ci_lo=estimate-ci,
         ci_hi=estimate+ci) %>%
  mutate(or=   exp(estimate),
         or_lo=exp(ci_lo),
         or_hi=exp(ci_hi)) %>%
  left_join(filter(dx_to_pde_table, year==2011), by=c('dx_cat', 'abx')) %>%
  mutate(rr=   risk_ratio_f(or,    f_with_abx),
         rr_lo=risk_ratio_f(or_lo, f_with_abx),
         rr_hi=risk_ratio_f(or_hi, f_with_abx)) %>%
  mutate(y=rr2pct(rr),
         ymin=rr2pct(rr_lo),
         ymax=rr2pct(rr_hi)) %>%
  mutate(change=sprintf('%.2f (%.2f -- %.2f)', y, ymin, ymax)) %>%
  select(dx_cat, abx, change, p.value)
```

```{r combined_table}
format_pct = function(x) format(round(x*100, 2), digits=2, nsmall=2)

@@

trends_by_demography = read_tsv('tables/demography_models.tsv') %>%
  filter(term=='year') %>%
  mutate(estimate=3*estimate,
         std.error=sqrt(3)*std.error) %>%
  mutate(ci=1.96*std.error,
         ci_lo=estimate-ci,
         ci_hi=estimate+ci) %>%
  mutate(y=est2pct(estimate),
         ymin=est2pct(ci_lo),
         ymax=est2pct(ci_hi)) %>%
  mutate(change=sprintf('%.2f (%.2f -- %.2f)', y, ymin, ymax)) %>%
  select(group_type, group, change, p.value)

>>>>

drug_trends = read_tsv('raw_data/poisson_models.tsv') %>%
  select(abx=model, term=Parameter, estimate=Estimate, std.error=StdErr, p.value=ProbChiSq) %>%
  filter(term=='year') %>%
  arrange(estimate) %>%
  mutate(estimate=3*estimate,
         std.error=sqrt(3)*std.error) %>%
  mutate(ci=1.96*std.error,
         ci_lo=estimate-ci,
         ci_hi=estimate+ci) %>%
  mutate(y=est2pct(estimate),
         ymin=est2pct(ci_lo),
         ymax=est2pct(ci_hi)) %>%
  mutate(change=sprintf('%.1f (%.1f -- %.1f)', y, ymin, ymax))
```

```{r drug_trends_display}
drug_trends %>%
  filter(abx != 'overall_wrefill') %>%
  select(abx, y, ymin, ymax, p.value) %>%
  mutate_at(vars(y, ymin, ymax), function(x) format(x, digits=1, nsmall=1)) %>%
  kable(caption='Drug trends: Percent change from 2011 to 2014')

drug_trends %>%
  # put the abx in order
  arrange(desc(y)) %>%
  mutate(abx=fct_inorder(factor(abx))) %>%
  mutate(abx=fct_relevel(abx, c('overall', 'overall_inapprop', 'overall_approp'))) %>%
  mutate(abx=fct_rev(abx)) %>%
  # plot
  ggplot(aes(x=abx, y=y, ymin=ymin, ymax=ymax)) +
  geom_bar(stat='identity', fill='white', color='black') +
  geom_errorbar(width=0.5) +
  coord_flip() +
  xlab('') +
  ylab('adjusted change in consumption 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 32.5), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_minimal() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```

@@

## Odds and stuff

```{r odds}
inapp_odds_trend = read_tsv('raw_data/logistic_models.tsv') %>%
  select(model, term=Variable, estimate=Estimate, std.error=StdErr, p.value=ProbChiSq) %>%
  filter(term=='year') %>%
  mutate(estimate=3*estimate,
         ci=1.96*sqrt(3)*std.error,
         y=exp(estimate),
         ymin=exp(estimate-ci),
         ymax=exp(estimate+ci)) %>%
  select(model, y, ymin, ymax) %>%
  mutate_if(is.numeric, function(x) round((x-1)*100, 1))

inapp_odds_trend %>% kable
```

@@

dx_to_pde_trends = read_tsv('tables/dx_to_pde_trends.tsv') %>%
  filter(term=='year') %>%
  mutate(estimate=3*estimate,
         std.error=sqrt(3)*std.error) %>%
  mutate(ci=1.96*std.error,
         ci_lo=estimate-ci,
         ci_hi=estimate+ci) %>%
  mutate(or=   exp(estimate),
         or_lo=exp(ci_lo),
         or_hi=exp(ci_hi)) %>%
  left_join(filter(dx_to_pde_table, year==2011), by=c('dx_cat', 'abx')) %>%
  mutate(rr=   risk_ratio_f(or,    f_with_abx),
         rr_lo=risk_ratio_f(or_lo, f_with_abx),
         rr_hi=risk_ratio_f(or_hi, f_with_abx)) %>%
  mutate(y=rr2pct(rr),
         ymin=rr2pct(rr_lo),
         ymax=rr2pct(rr_hi)) %>%
  mutate(change=sprintf('%.1f (%.1f -- %.1f)', y, ymin, ymax)) %>%
  select(dx_cat, abx, change, p.value)
```

```{r combined_table}
format_pct = function(x) format(round(x*100, 1), digits=1, nsmall=1)
format_p = function(p) if_else(p<0.0001, '<.0001', format(round(p, 4), digits=4, nsmall=4))

@@

trends_by_demography = read_tsv('tables/demography_models.tsv') %>%
  filter(term=='year') %>%
  mutate(estimate=3*estimate,
         std.error=sqrt(3)*std.error) %>%
  mutate(ci=1.96*std.error,
         ci_lo=estimate-ci,
         ci_hi=estimate+ci) %>%
  mutate(y=est2pct(estimate),
         ymin=est2pct(ci_lo),
         ymax=est2pct(ci_hi)) %>%
  mutate(change=sprintf('%.1f (%.1f -- %.1f)', y, ymin, ymax)) %>%
  select(group_type, group, change, p.value)
